---
title: "Week 03 `dplyr` Activity"
author: "**[[**Your Name**]]**"
format: gfm
---

## Home Mortgage Disclosure Act (HMDA) Data

This data is collected from the [Consumer Financial Protection Bureau](https://www.consumerfinance.gov/data-research/hmda/historic-data/?geo=nationwide&records=all-records&field_descriptions=labels), who give the following summary.

> Each year thousands of financial institutions report data about mortgages to
the public, under the Home Mortgage Disclosure Act (HMDA). We provide the data
collected under HMDA from 2007-2017 for download.
> For mortgage applications, the data will tell you if the consumer got the
mortgage—look for applications that were "originated"—or if the consumer was
denied, didn't complete the application, or something else happened. The data
also have information about pre-approvals and loans sold from one institution to
another. For each record, you can learn about the loan, the property
characteristics, the applicant demographics, and the lender. The data are
modified to protect applicant and borrower privacy.



```{r}
suppressPackageStartupMessages(library(tidyverse))
hmda_s <- read_rds("hmda_2014-17_sample_80k.rds") |>
  select(-agency_code)
unique_vals <- hmda_s |>
  summarize(a = across(where(is_character), \(f) list(unique(f)))) |>
  unnest(a) |>
  pivot_longer(everything()) |>
  filter(!(name %in% c("state", "county", "state_abbr", "msamd"))) |>
  unnest(value) |>
  group_by(value) |>
  slice_head(n = 1) |>
  arrange(name)
unique_vals
```

The table above has all the unique values for the different columns, except for
the location variables.




```{r}
hmda_s |>
  mutate(denied = !is.na(denial_reason_1)) |>
  ggplot(aes(
    y = as_factor(as_of_year),
    x = applicant_income_000s,
    color = denied
  )) +
  geom_boxplot() +
  scale_x_log10() +
  scale_y_discrete(guide = guide_axis(angle = 45))
```

## Activity

I recommend iterating between 1, 2 and 3. The first question you ask might be too complicated or too simple. Try to come up with an interesting 

1. What question do you want to ask about the data?
2. Use `dplyr` verbs make a table that tries to address the question.
3. Make a plot using `dplyr` verbs and `ggplot` that tries to address the question.
4. Describe your observation. If you feel you were able to answer your question, what is the answer?
5. What were you unable to do that you think you could do with this data?
6. What other data would you want to incorporate into this data?
